Stochastic Variance Reduced Policy Gradient

### 2018-02-01 svrpg.tex
Modified Hypermarapeters section

\section{Stopping Condition}\label{sec:stopping}
As shown, the performance of the SVRPG algorithm is sensitive to the number of sub-iterations.
As the number of sub-iterations increases, the variance of the importance weights and the gradient increases too.
Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.
A fixed number of sub-iterations is not the optimal choice.
Few sub-iterations lead to few updates, many update lead to increases of variance.

We introduce two stopping condition: the maximum number of sub-iterations and the condition on learning rate of Adam sub-iterations.
Adam update rule help to stabilize the gradient estimate. In fact, this method computes adaptive learning rates for each parameter that depends on the history of the gradients' variance.
In particular we use two different Adam parameters: the first one for snapshot updates and the second one for the sub-iterations updates.
We stop with sub-iterations if:

>>>>

\section{Hyperparameters}\label{sec:stopping}
In Reinforcement learning we have to take into account the gradient's variance.
A used way for reduce the effect of variance is to use Adaptive Moment Estimation (Adam) \cite{kingma2015adam}, a method that computes adaptive learning rates for each parameter. Adam help to stabilize the gradient estimate. In fact, this method computes adaptive learning rates for each parameter that depends on the history of the gradients' variance.
We use two different adam hyperparameters: one for updates tied to Snapshots points and the other tied to the updates of sub-iterations points. 
This is because we're dealing with two different variance dimensions.
Denote by $\alpha_{snap}$ the last learning rate computed into the snapshot point and denote by  $\alpha_{sub-iter}$ the last learning rate computed into the sub-iteration point.

As shown, the performance of the SVRPG algorithm is sensitive to the number of sub-iterations.
As the number of sub-iterations increases, the variance of the importance weights and the gradient increases too.
Therefore, the SVRPG algorithm fails in its primary aim of stabilizing the gradient estimate.
A fixed number of sub-iterations is not the optimal choice.
Few sub-iterations lead to few updates, many update lead to increases of variance.

We introduce two stopping condition: the maximum number of sub-iterations and the condition on learning rate of Adam sub-iterations.
We stop with sub-iterations if:
